Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

Finding the $\cross_H(r^*)$ sets of all $r^* \in R^*_i$ is an instance of the find-all-sorted version of Problem $\mathscr{D}$. Statement (1) of the above lemma assures us that the total time to do so for all $R^*_1, ..., R^*_{k-2}$ is $O(n \log n + \out)$. Note that, for each $\cross_H(r^*)$ computed, the (horizontal) segments therein has been sorted in ascending order of y-coordinate.

@@

\extraspacing {\bf Computing the ``d-cross'' Sets.}

>>>>

@@

Finding the $\cross_H(r^*)$ sets of all $r^* \in R^*_i$ is an instance of the find-all-sorted version of Problem $\mathscr{D}$. Statement (1) of the above lemma assures us that the total time to do so for all $R^*_1, ..., R^*_{k-2}$ is bounded by $O(n \log n + \out)$. Note that, for each $\cross_H(r^*)$ computed, the (horizontal) segments therein has been sorted in ascending order of y-coordinate.

\extraspacing {\bf Computing the ``d-cross'' Sets.} We are ready explain how to compute $\dcross_H(\bm{t})$ for any $\bm{t} \in \J(R'_1, ..., R'_{k-2})$. By Statement (2) of Lemma~\ref{lmm:hv:type1:cross-r*},
